Final Project - Stroke Predictions

### 2021-05-14 draft.Rmd
updates

# Methods and Evaluation
Do evaluation with each method, not all after

•	Methods – Techniques you are using to address your question and the results of those methods.
•	Evaluation of your model – Select appropriate metrics and explain the output as it relates to your question.

@@

@@

The top five for MDA are: Age, BMI, Heart Disease, Marriage, and Hyper Tension with all five being 3 or higher

@@

The top five for MDG are: Age, Glucose Level, BMI, Heart Disease and Hyper Tension with the first three being much higher (4-6 times)

@@

# create the random forest
stroke_rf_4 = randomForest(
  as.factor(stroke)~.,
  stroke_factor_training_data,
  #y = NULL,           #<- A response vector. This is unnecessary because we're specifying a response formula.
  #subset = NULL,      #<- This is unnecessary because we're using all the rows in the training data set.
  #xtest = NULL,       #<- This is already defined in the formula by the ".".
  #ytest = NULL,       #<- This is already defined in the formula by "parent".
  ntree = 4,        #<- Number of trees to grow. This should not be set to too small a number, to ensure that every input row gets classified at least a few times.
  mtry = mytry_tune(stroke_factor_training_data),            #<- Number of variables randomly sampled as candidates at each split. Default number for classification is sqrt(# of variables). Default number for regression is (# of variables / 3).
  replace = TRUE,      #<- Should sampled data points be replaced.
  #classwt = NULL,     #<- Priors of the classes. Use this if you want to specify what proportion of the data SHOULD be in each class. This is relevant if your sample data is not completely representative of the actual population 
  #strata = NULL,      #<- Not necessary for our purpose here.
  sampsize = 100,      #<- Size of sample to draw each time.
  nodesize = 10,        #<- Minimum numbers of data points in terminal nodes.
  #maxnodes = NULL,    #<- Limits the number of maximum splits. 
  importance = TRUE,   #<- Should importance of predictors be assessed?
  #localImp = FALSE,   #<- Should casewise importance measure be computed? (Setting this to TRUE will override importance.)
  proximity = FALSE,    #<- Should a proximity measure between rows be calculated?
  norm.votes = TRUE,   #<- If TRUE (default), the final result of votes are expressed as fractions. If FALSE, raw vote counts are returned (useful for combining results from different runs).
  do.trace = TRUE,     #<- If set to TRUE, give a more verbose output as randomForest is run.
  keep.forest = TRUE,  #<- If set to FALSE, the forest will not be retained in the output object. If xtest is given, defaults to FALSE.
  keep.inbag = TRUE   #<- Should an n by ntree matrix be returned that keeps track of which samples are in-bag in which trees? 
)
```

@@

The top five for MDA are: Age, BMI, Gender, Heart Disease, and Hyper Tension.

What is interesting is that we are now seeing a negative or zero impact from some of the parameters, we will remove these and compare below. The largets parameters to consider later are Age, Gender and Heart Disease.

The top three for MDG are: Glucose Level, Age, and BMI. All other parameters have a score of 0.5 or lower and will not be considered.

@@

# create the random forest
stroke_rf_lean = randomForest(
  as.factor(stroke)~.,
  stroke_factor_training_data_lean,
  #y = NULL,           #<- A response vector. This is unnecessary because we're specifying a response formula.
  #subset = NULL,      #<- This is unnecessary because we're using all the rows in the training data set.
  #xtest = NULL,       #<- This is already defined in the formula by the ".".
  #ytest = NULL,       #<- This is already defined in the formula by "parent".
  ntree = 4,        #<- Number of trees to grow. This should not be set to too small a number, to ensure that every input row gets classified at least a few times.
  mtry = mytry_tune(stroke_factor_training_data_lean),            #<- Number of variables randomly sampled as candidates at each split. Default number for classification is sqrt(# of variables). Default number for regression is (# of variables / 3).
  replace = TRUE,      #<- Should sampled data points be replaced.
  #classwt = NULL,     #<- Priors of the classes. Use this if you want to specify what proportion of the data SHOULD be in each class. This is relevant if your sample data is not completely representative of the actual population 
  #strata = NULL,      #<- Not necessary for our purpose here.
  sampsize = 100,      #<- Size of sample to draw each time.
  nodesize = 10,        #<- Minimum numbers of data points in terminal nodes.
  #maxnodes = NULL,    #<- Limits the number of maximum splits. 
  importance = TRUE,   #<- Should importance of predictors be assessed?
  #localImp = FALSE,   #<- Should casewise importance measure be computed? (Setting this to TRUE will override importance.)
  proximity = FALSE,    #<- Should a proximity measure between rows be calculated?
  norm.votes = TRUE,   #<- If TRUE (default), the final result of votes are expressed as fractions. If FALSE, raw vote counts are returned (useful for combining results from different runs).
  do.trace = TRUE,     #<- If set to TRUE, give a more verbose output as randomForest is run.
  keep.forest = TRUE,  #<- If set to FALSE, the forest will not be retained in the output object. If xtest is given, defaults to FALSE.
  keep.inbag = TRUE   #<- Should an n by ntree matrix be returned that keeps track of which samples are in-bag in which trees? 
)
```

>>>>

# Methods and Evaluation

@@

stroke_positive <- subset(stroke, stroke == 1)
stroke_negative <- subset(stroke, stroke == 0)
stroke_sample <- stroke_negative[sample(1:nrow(stroke_negative), size = 180),]
stroke <- rbind(stroke_sample, stroke_positive)

@@

The top five for MDA are: Age, BMI, Heart Disease, Marriage, and Hyper Tension

@@

The top five for MDG are: Age, Glucose Level, BMI, Heart Disease and Hyper Tension

We see that age is much more important than the rest of the factors for both plots.

@@

# create the random forest
stroke_rf_4 = randomForest(
  as.factor(stroke)~.,
  stroke_factor_training_data,
  #y = NULL,           #<- A response vector. This is unnecessary because we're specifying a response formula.
  #subset = NULL,      #<- This is unnecessary because we're using all the rows in the training data set.
  #xtest = NULL,       #<- This is already defined in the formula by the ".".
  #ytest = NULL,       #<- This is already defined in the formula by "parent".
  ntree = 200,        #<- Number of trees to grow. This should not be set to too small a number, to ensure that every input row gets classified at least a few times.
  mtry = mytry_tune(stroke_factor_training_data),            #<- Number of variables randomly sampled as candidates at each split. Default number for classification is sqrt(# of variables). Default number for regression is (# of variables / 3).
  replace = TRUE,      #<- Should sampled data points be replaced.
  #classwt = NULL,     #<- Priors of the classes. Use this if you want to specify what proportion of the data SHOULD be in each class. This is relevant if your sample data is not completely representative of the actual population 
  #strata = NULL,      #<- Not necessary for our purpose here.
  sampsize = 100,      #<- Size of sample to draw each time.
  nodesize = 10,        #<- Minimum numbers of data points in terminal nodes.
  #maxnodes = NULL,    #<- Limits the number of maximum splits. 
  importance = TRUE,   #<- Should importance of predictors be assessed?
  #localImp = FALSE,   #<- Should casewise importance measure be computed? (Setting this to TRUE will override importance.)
  proximity = FALSE,    #<- Should a proximity measure between rows be calculated?
  norm.votes = TRUE,   #<- If TRUE (default), the final result of votes are expressed as fractions. If FALSE, raw vote counts are returned (useful for combining results from different runs).
  do.trace = TRUE,     #<- If set to TRUE, give a more verbose output as randomForest is run.
  keep.forest = TRUE,  #<- If set to FALSE, the forest will not be retained in the output object. If xtest is given, defaults to FALSE.
  keep.inbag = TRUE   #<- Should an n by ntree matrix be returned that keeps track of which samples are in-bag in which trees? 
)
```

@@

We are seeing very similar plots than we did before with the larger model.

@@

# create the random forest
stroke_rf_lean = randomForest(
  as.factor(stroke)~.,
  stroke_factor_training_data_lean,
  #y = NULL,           #<- A response vector. This is unnecessary because we're specifying a response formula.
  #subset = NULL,      #<- This is unnecessary because we're using all the rows in the training data set.
  #xtest = NULL,       #<- This is already defined in the formula by the ".".
  #ytest = NULL,       #<- This is already defined in the formula by "parent".
  ntree = 200,        #<- Number of trees to grow. This should not be set to too small a number, to ensure that every input row gets classified at least a few times.
  mtry = mytry_tune(stroke_factor_training_data_lean),            #<- Number of variables randomly sampled as candidates at each split. Default number for classification is sqrt(# of variables). Default number for regression is (# of variables / 3).
  replace = TRUE,      #<- Should sampled data points be replaced.
  #classwt = NULL,     #<- Priors of the classes. Use this if you want to specify what proportion of the data SHOULD be in each class. This is relevant if your sample data is not completely representative of the actual population 
  #strata = NULL,      #<- Not necessary for our purpose here.
  sampsize = 100,      #<- Size of sample to draw each time.
  nodesize = 10,        #<- Minimum numbers of data points in terminal nodes.
  #maxnodes = NULL,    #<- Limits the number of maximum splits. 
  importance = TRUE,   #<- Should importance of predictors be assessed?
  #localImp = FALSE,   #<- Should casewise importance measure be computed? (Setting this to TRUE will override importance.)
  proximity = FALSE,    #<- Should a proximity measure between rows be calculated?
  norm.votes = TRUE,   #<- If TRUE (default), the final result of votes are expressed as fractions. If FALSE, raw vote counts are returned (useful for combining results from different runs).
  do.trace = TRUE,     #<- If set to TRUE, give a more verbose output as randomForest is run.
  keep.forest = TRUE,  #<- If set to FALSE, the forest will not be retained in the output object. If xtest is given, defaults to FALSE.
  keep.inbag = TRUE   #<- Should an n by ntree matrix be returned that keeps track of which samples are in-bag in which trees? 
)
```
